Estimating migration rates for iteroparous species using kinship pairs found between populations\protect\thanks{Running head line: Estimating migration rates using kinship pairs}

### 2021-06-22 latex/ms.tex
modify Fig and count parameters
write theory section, #6

\section{Theory}\label{sec2}
In this section, we derivate the estimators of migrant number and migration rates using HS pairs or PO pairs found between two populations. While the estimators can hold under complex assumptions for reproduction theoretical foundation for estimating
このセクションでは、migrantやmigration rateの推定量を導出する。導出された推定量は、付録にある通りフレキシブルな仮定のもとでも成立するが、ここではシンプルな状況を例に出して説明する。The main symbols used in the current paper are summarized in Table \ref{symbols}.

@@

%%%FIGURE 1%%%
\begin{figure}[!h]
	\begin{center}
		\includegraphics[width=0.3\textwidth]{/Users/akita/Dropbox/research/close_kin/Mig/Figs/cartoon.eps}
		\caption{Example of relationships between mothers and their offspring number. The open, gray, and filled circles represent mothers, their eggs, and their offspring, respectively. The area of an open circle indicates the degree of reproductive potential of each mother (i.e., $\lambda_i$). The dotted and thin arrows denote mother--egg and egg--offspring relationships, respectively. The symbol x denotes a failure to survive at sampling. Sampled individuals are denoted with squares. In this example, $M=6$, }
		\label{cartoon}
	\end{center}
\end{figure}
%%%%%%%%%%%

>>>>

\section{Theory}\label{sec2}
In this section, we present the theoretical foundation for estimating a migrant number and a migration rate using HS or PO pairs, which are found between two populations with a different sample timing. While the estimators can hold under flexible assumptions for reproduction (see {\bf Appendix}), here we assume a relatively simple situation for explanation purposes. It should be noted that the formulation of the estimators, presented in Equations 4-5 and 7-8, is a function with parent numbers in the two populations; in the next section, we provide the treatment for estimating the unknown parent numbers from genetic dataset which is used for obtaining HS or PO pairs. The main symbols used in the current paper are summarized in Table \ref{symbols}.

@@

%%%FIGURE 1%%%
\begin{figure}[!h]
	\begin{center}
		\includegraphics[width=0.3\textwidth]{/Users/akita/Dropbox/research/close_kin/Mig/Figs/cartoon.eps}
		\caption{Example of relationships between mothers and their offspring number. The open, gray, and filled circles represent mothers, their eggs, and their offspring, respectively. The area of an open circle indicates the degree of reproductive potential of each mother (i.e., $\lambda_i$). The dotted and thin arrows denote mother--egg and egg--offspring relationships, respectively. The symbol x denotes a failure to survive at sampling. Sampled individuals are denoted with squares. Input parameters in this example: $n_{\rm P, 1}=4$, $n_{\rm P, 2}=4$, $n_{\rm O, 1}=4$, $n_{\rm O, 2}=4$, $N_{1}=16$, $N_{2}=14$, and $M=6$. The numbers of kinship pairs: $H_{\rm PO, 1}=1$, $H_{\rm PO, 2}=1$, $H_{\rm PO, bet}=1$, and $H_{\rm HS, bet}=2$.	}
		\label{cartoon}
	\end{center}
\end{figure}
%%%%%%%%%%%
